Security on Networks

### 2013-05-15 paper/paper.tex
finished recursive algorithm stuff.

The problem with the naive scheme is that it wastes potential information which might be useful. For example,

>>>>

The problem with the naive scheme is that it wastes potential information which might be useful. For example, the minimum cut between nodes $u$ and $v$ will also be the minimum cut between either $u$ or $v$ and another node $w$. This is true because there will be at least one other node in either $u$ or $v$'s partition. Note that the size $|U|$ of $u$'s partition $U$ can be related to $|V|$, the size of $v$'s partition $V$, by the expression $n = |U| + |V|$. Thus, even if $U$ only contains a single element, $V$ will contain $n-1$ elements. This simple exercise has shown that there is a large amount of repeated information between minimum cuts computed for different nodes.

In fact, we can show that one can find all the minimum cuts using the Recursive Contraction Algorithm in the same time that it takes to find a single minimum cut. Karger and Stein (1996) show that the probability $P(n)$ of a specific cut is given by $P(n) = O(1/ \ln n)$.

\begin{theorem}
Using the Recursive Contraction Algorithm, one can find all min cuts with probability of missing any min cut at $O(1/n)$ in a running time of $O(n^2 \ln^3 n)$.
\end{theorem}
\begin{proof}
Running the Recursive Contraction Algorithm takes $O(n^2 \ln n)$ time, as described by Karger and Stein (1996), so it takes $O(n^2 \ln^3 n)$ time to run the algorithm $O( \ln^2 n)$ times. It remains to be shown that running the algorithm $O(\ln^2 n)$ times will bound the probability of missing any minimum cut by $O(1/n)$.

We know however that there are at most ${n \choose 2}$ min cuts, because each min cut must contain two partitioned sets of vertices. Moreover, the probability of not finding a specific cut $k$ is given by:
\begin{eqnarray}
  Pr[\textrm{miss }k] = (1 - P(n))^{O( \ln^2 n)} \leq \left(1 - \frac{c}{\ln n} \right)^{\frac{3 \ln^2 n}{c}} \leq e^{-3 \ln n} = \frac{1}{n^3}
\end{eqnarray}

There are at most ${n \choose 2}$ possible min cuts $k$. Since finding each one of these min cuts is independent, the probability of missing any of the min cuts is
\begin{eqnarray}
  {n \choose 2} \frac{1}{n^3} \leq \frac{n^2}{2} \frac{1}{n^3} = O \left( \frac{1}{n} \right)
\end{eqnarray}
\end{proof}
